### 2014-07-31 fundamentals/impl.tex
more content and comments added in intro, examples, impl, and verification

Only a modular, agent-based approach is capable of adequately solving system 
dynamics problems involving material routing, facility deployment, regional and 
institutional hierarchies.

@@

Not many fuel cycle simulators have this, it turns out. We used to implement 
this with inheritance. Now I'm not so sure. . . <insert recent knowledge here>.

@@

The toolkit is a place for developers and users to contribute common-use tools 
for calculating metrics, managing process physics, handling data.

This was implemented by liberal use of namespaces  and is populated with an 
introductory suite of useful tools.

@@

Cycamore contains a number of usefule facility models that are a mere base-set. 
Additional modules are needed for full fuel cycle simulation. However, simple 
fuel cycles can be generated with Cycamore and Cyclus alone.

>>>>

A modular, agent-based is an ideal approach for solving complicated
physics-dependent supply chain problems involving material routing, facility
deployment, regional and institutional hierarchies.

@@

Cyclus has three core agent classes that be subclassed to create a simulation
archetype: Region, Institution, and Facility. At present, Regions, Institutions,
and Facilities (RIF) conceptually form a nested structure in a Cyclus simulation,
i.e., Facilities exist in (i.e., are managed by) Institutions and Institutions
exist in Regions.

Importantly, the RIF separation allows for preferential trading. For example,
Facilities in the same Institution can preferentially trade with each
other. Similarly, Regions can be given a location proxy, and the trade between
Facilities can be informed by their regional proximity.

@@

The toolkit is a place for developers and users to contribute common-use tools 
for calculating metrics, managing process physics, and handling data.

This was implemented by liberal use of namespaces and is populated with an
introductory suite of useful tools, including helper classes for managing
facility deployment, minimum cost facility deployment decision making, and for
enrichment-related calculations.

@@

Cycamore contains a number of usefule facility models that are a mere base-set.
Additional modules are needed for interesting fuel cycle simulation. However,
simple, once-through fuel cycles can be generated with Cycamore and Cyclus alone.

### 2014-07-31 fundamentals/intro.tex
more topic sentences
more content and comments added in intro, examples, impl, and verification

@@

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform.

@@

Previous simulators have been static or dynamic. Some have been discrete while 
others have been fleet-based. Some have captured regional behavior, material 
isotopics, transmutation detail, etc. Indeed, some tools have attempted 
agent-based functionality.

@@

@@

@@

@@

ABM is modern, sophisticated, true to reality, and it takes advantage of modern 
computing resources.

@@

>>>>

% MJG - I'm hesitant about using the phrase 'full detail'. I think we can be
% more precise.

@@

An alternative to these approaches is a dynamic, agent-based simulator with an 
free, openly accessible simulation-logic kernel.

@@

% MJG - We need to be very precise about the terms 'static' and 'dynamic'. They
% should likely be defined before being used in this context.

Previous simulators have been static or dynamic. Some have been discrete while 
others have been fleet-based. Some have captured regional behavior, material 
isotopics, transmutation detail, etc. Indeed, some tools have attempted 
agent-based functionality. % MJG - Which ones? The closest I can think of is
                           % NFCSim, and it's implementation details are closed.

@@

% MJG - @gonuke has always cited method-to-method comparisons as the primary
% benefit Cyclus can bring to the table. Do we want to frame the hero narrative
% in that context? The more I think about, the more I feel like this is a
% secondary argument. I'll take a crack at a few sentences below.

@@

% MJG - I don't claim that all of this belongs in the beginning of this
% subsection, but here's some more content.

Modeling the growth of a physics-dependent, international nuclear fuel supply
chain is a difficult problem. To date, it has been treated relatively
lightly. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition fast reactor fuel. Accordingly, each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels either impossible or difficult and time consuming.

Cyclus uses a divide-and-conquer approach, separating the problem of modeling a
physics-dependent supply chain into a simulation kernel and archetypes that
interact with the kernel during a simulation. The kernel is responsible for the
deployment and interaction logic of entities in the simulation. Physics
calculations are constrained to individual archetypes. Accordingly, specialists
in a given field can utilize their time and resources in modeling a specific
process associated with the nuclear fuel cycle, e.g. reprocessing and advance
fuel fabrication, rather than also modeling the entirety of the cycle.

% we could use a specific example of Cosi's equivalence method below
Because Cyclus uses a modular archetype approach, comparing two archetypes is
straightforward. Consider a case in which an analyst would like to compare the
effect of using different models to determining input fuel composition for fast
reactors. A variety fuel fabrication archetypes can be developed and used
interchangably to analyze the effect of each on a simulation's output.

@@

We expect that there are a number of types of users and developers who will 
interact with the Cyclus framework. Those people fall into a number of 
categories. All such people benefit from the modular architecture.

% man that figure has gone quite a ways =)
<modified-open-source collaboration diagram>

@@

ABM is modern, sophisticated, true to reality, and it takes advantage of modern
computing resources. Furthermore, agent-based modeling provides an analyst a
more natural perspective from which to model a given problem. In the nuclear
fuel cycle context for example, an analyst can design an agent with
reactor-related logic and a separate agent with fuel fabrication-related logic.

System dynamics popular approach for modeling nuclear fuel cycles in current
tools (cite VISION/CAFCA). It has been shown in the literature
\cite{macal_agent-based_2010} that any system dynamics model can be translated
into an agent-based model. Furthermore, it has been shown that agent-based
techniques can provide a richer model than can system dynamics. Formally, the
set of system dynamics models is a strict subset of agent-based models.

@@

A discrete resource model allows for a range of modeling granularity. In the
macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
microscopic extreme, the model is capable of representing individual fuel
assemblies.
